---
title: "Penguins Exploratory Data Analysis"
format:
  html:
    code-fold: true
---

## Penguin Size and Mass by Sex and Species

```{r}
#| message: false
library(palmerpenguins)
library(dplyr)
library(ggplot2)
library(dbplyr)

df <- palmerpenguins::penguins
```

```{r}
#| message: false 
df %>%
  group_by(species, sex) %>%
  summarise(
    across(
      where(is.numeric), 
      \(x) mean(x, na.rm = TRUE)
      )
    ) %>%
  knitr::kable()
```

## Penguin Size vs Mass by Species

```{r}
#| message: false 
#| warning: false
df %>%
  ggplot(aes(x = bill_length_mm, y = body_mass_g, color = species)) +
  geom_point() + 
  geom_smooth(method = "lm")
```
In general, this graph demonstrates that the species predictor has a strong relationship with the bill_length_mm and body_mass_g. For Adelie penguins, there seems to be bill_length_mm and body_mass_g values on the lower end suggesting that the Adelie species is typically a smaller type of penguin. The Chinstrap seems to demonstrate longer bill_length_mm but similar body_mass_g meaning that these penguins are similar size to Adelie penguins but with a proportionally longer bill. Finally, the Gentoo penguins show generally higher body_mass_g than both species and bill_length_mm similar to the Chinstrap species. This tells us that likely these are the biggest penguin species of thr three and have bill legnths proportionally closer to the Adelie penguins.

## Penguin Size vs Mass by Sex
```{r}
#| message: false 
#| warning: false

df_new<-df[complete.cases(df$sex), ]
df_new %>%
  ggplot(aes(x = bill_length_mm, y = body_mass_g, color = sex)) +
  geom_point() + 
  geom_smooth(method = "lm")
```
The line of best fit for the two sexes are relatively parallel demonstrating that the overall proportion of bill_length_mm and body_mass_g have similar results between male and female penguins. Looking at the individual data points, it seems that, on the extreme ends of body_mass_g, males tend to lie in the high zone and females in the low. In the center of the body_mass_g range, there is a good mix. This demonstrates that sex may not be the only delineating factor in correlated body_mass_g. As seen above, the interplay of species also has a big play in the mass of a penguin. In terms of bill_length_mm, there seems to be an even spread across the range for both sexes. Overall, this graph shows a weaker relationship between bill_length_mm and body_mass_g, and sex in comparison to the relationship show above with bill_length_mm and body_mass_g, and sex.

## Data Processing

```{r}
#| message: false 
df %>%
  group_by(species, sex) %>%
  summarise(
    across(
        ends_with("mm") | ends_with("g"),
      \(x) mean(x, na.rm = TRUE)
      )
    ) %>%
  dplyr::collect() %>%
  knitr::kable()
```

<!--
# ```{r}
# #connecting to the database
# library(dbplyr)
# con <- DBI::dbConnect(
#   duckdb::duckdb(), 
#   dbdir = "my-db.duckdb"
#   )
# ```
# 
# ```{r}
# DBI::dbWriteTable(con, "penguins", palmerpenguins::penguins)
# df <- dplyr::tbl(con, "penguins")
# ```
# 
# ```{r}
# req <- httr2::request("http://127.0.0.1:8080/predict") |>
#   httr2::req_body_json(
#     list(
#       list(
#         "bill_length_mm" = 0,
#         "species_Chinstrap" = FALSE,
#         "species_Gentoo" = FALSE,
#         "sex_male" = FALSE
#       )
#     )
#   ) |>
#   httr2::req_perform()
# res <- httr2::resp_body_json(req)$predict[[1]]
# ```
# 
# ```{r}
# DBI::dbDisconnect(con)
```
-->
